A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-27 UAM2014/Article/article.tex
la2pdf commit - 2014:04:28	00:51:19	(Mon28.Apr)

% \usepackage{caption}
\usepackage{subcaption}

@@

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_cylinder_submerged.svg}%
\caption{Overlay.}\label{overlay_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[width=\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
\caption{Overlay (adaptive).}\label{overlay_cylinder_adaptive}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_colors.svg}%
\caption{Overlay.}\label{overlay_cylinder}%
\end{figure}

>>>>

% \usepackage{caption}
\usepackage{subcaption}
\usepackage{color}

@@

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}%
\caption{Simulator.}\label{buildup}%
\end{figure}

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Simulated cylinder (adaptive).}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive_bw.svg}%
\caption{Simulated cylinder (adaptive).}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

\newcommand\cdesc[2]{{\raggedright\setlength\fboxsep{0pt}
\fbox{\colorbox[HTML]{#1}{\vrule height8.5pt depth3.5pt width0pt\hspace{.5cm}}}\ \ #2\\}}
\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_cylinder_submerged.svg}%
\caption{Overlay.}\label{overlay_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[width=\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
\caption{Overlay (adaptive).}\label{overlay_cylinder_adaptive}%
\end{subfigure}
\hfill\parbox{\linewidth-30pt}{
\cdesc{800000}{Pixels in both template and image highlight segments}
\cdesc{FF1000}{Pixels only in template highlight segment}
\cdesc{FFEB00}{Pixels only in image highlight segment}
\cdesc{83FF7C}{Background pixels}
\cdesc{00EFFF}{Pixels only in the image shadow segment}
\cdesc{00A7FF}{Pixels in the image segment, but in template shadow}
\cdesc{0014FF}{Pixels only in the image template highlight segment}
\cdesc{000083}{Pixels in both the template and image shadow segments}}
\end{figure}
